\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
better wording.
replace latin, better to not risk confusion

\section{Quality assurance}
The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx, a 
Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages 
available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
and \pyinline{pyg4ometry.pycgal} in C++. \PYGEOMETRY{} package dependencies and extensions are installed easily using 
\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using software tests, of which 543 tests are available 
for the code, which have 84\% coverage. The tests also serve as minimal examples to help users understand the code operation.

\section{Conclusions and discussion}
The authors believe that tools to quickly create, either ab initio or by conversion geometry usable in Monte Carlo
particle transport programmes will save significant amounts of user effort and ultimately 
yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 
creation tool, whilst heavily internally based on Geant4 and GDML, it can have utility for users of all MCRT 
codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. Presently it provides a coherent and 
uniform interface to existing tools and utilities, also by using the Python programming language \PYGEOMETRY{} 
allows the programmatic control of geometry creation or modification. This approach allows the integration of 
other available tools \cite{DavisNIMA915-65} into an unified workflow.

>>>>

\section{Quality assurance}
The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx, a 
Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages 
available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
and \pyinline{pyg4ometry.pycgal} in C++. \PYGEOMETRY{} package dependencies and extensions are installed easily using 
\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using software tests, of which 543 are available,  
resulting in 84\% code coverage. The tests also serve as minimal examples to help users understand the code operation.

\section{Conclusions and discussion}
The authors believe that tools to quickly create, either from scratch or by conversion geometry usable in Monte Carlo
particle transport programmes will save significant amounts of user effort and ultimately 
yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 
creation tool, whilst heavily internally based on Geant4 and GDML, it can have utility for users of all MCRT 
codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. Presently it provides a coherent and 
uniform interface to existing tools and utilities, also by using the Python programming language \PYGEOMETRY{} 
allows the programmatic control of geometry creation or modification. This approach allows the integration of 
other available tools \cite{DavisNIMA915-65} into an unified workflow.
